% ============================================================
%  bibliography.tex -- список литературы
% ============================================================

\addcontentsline{toc}{section}{Список литературы}

\begin{thebibliography}{99}

\bibitem{abramowitz}
  Абрамовиц М., Стиган И.
  \textit{Справочник по специальным функциям.}
  Наука, 1979.

\bibitem{voller1987}
  Voller~V.\,R., Cross~M., Markatos~N.\,C.
  An enthalpy method for convection/diffusion phase change~//
  International Journal for Numerical Methods in Engineering.~---
  1987.~--- Vol.~24.~--- P.~271--284.

\bibitem{voller1981}
  Voller V.R., Cross M.
  \textit{Accurate solutions of moving boundary problems using the enthalpy method.}
  International Journal of Heat and Mass Transfer, 1981, vol.~24, pp.~545--556.

\bibitem{fabbro1990}
  Fabbro R., Fournier J., Ballard P., Devaux D., Virmont J.
  \textit{Physical study of laser-produced plasma in confined geometry.}
  Journal of Applied Physics, 1990, vol.~68, pp.~775--784.

\bibitem{peyre1995}
  Peyre P., Fabbro R.
  \textit{Laser shock processing: a review of the physics and applications.}
  Optical and Quantum Electronics, 1995, vol.~27, pp.~1213--1229.

\bibitem{carslaw1959}
  Carslaw~H.\,S., Jaeger~J.\,C.
  Conduction of Heat in Solids.~--- 2nd~ed.~---
  Oxford: Clarendon Press, 1959.

\bibitem{patankar1980}
  Patankar S.V.
  \textit{Numerical Heat Transfer and Fluid Flow.}
  Hemisphere Publishing, 1980.

\bibitem{vtk}
  Schroeder W., Martin K., Lorensen B.
  \textit{The Visualization Toolkit.}
  Kitware, 4th ed., 2006.

\bibitem{fenics}
  Logg A., Mardal K.-A., Wells G.
  \textit{Automated Solution of Differential Equations by the Finite Element Method.}
  Springer, 2012.

\bibitem{biot1956}
  Biot M. A.
  \textit{Thermoelasticity and Irreversible Thermodynamics.}
  Journal of Applied Physics, 27(3):240--253, 1956.
  \href{https://doi.org/10.1063/1.1722402}{doi:10.1063/1.1722402}.

\bibitem{mises1913}
  von Mises R.
  \textit{Mechanik der festen Koerper im plastisch-deformablen Zustand.}
  Nachrichten von der Gesellschaft der Wissenschaften zu Goettingen,
  Mathematisch-Physikalische Klasse, 1913, pp. 582--592.
  \href{https://neo-classical-physics.info/uploads/3/4/3/6/34363841/von_mises_-_plastic_deformation.pdf}{PDF}.

\bibitem{hfaiedh2015}
  Hfaiedh N., Peyre P., Song H., Popa I., Ji V., Vignal V.
  \textit{Finite element analysis of laser shock peening of 2050-T8 aluminum alloy.}
  International Journal of Fatigue, 70:480--489, 2015.
  \href{https://doi.org/10.1016/j.ijfatigue.2014.05.015}{doi:10.1016/j.ijfatigue.2014.05.015}.

\bibitem{lab3fenicsrepo}
  TheEntityCircle.
  \textit{miniscience-4th-term: 03\_fenics/python.}
  GitHub repository.
  \href{https://github.com/TheEntityCircle/miniscience-4th-term/tree/master/2025/03_fenics/python}{github.com/TheEntityCircle/miniscience-4th-term}.

\bibitem{miniscience-labs}
  TheEntityCircle.
  \textit{Лабораторные работы курса «Научные вычисления» (4-й семестр).}
  GitHub, 2025.
  \url{https://github.com/TheEntityCircle/miniscience-4th-term/tree/master/2025}

\bibitem{miniscience-microproject}
  TheEntityCircle.
  \textit{Микропроект курса «Научные вычисления» (4-й семестр): примеры задач.}
  GitHub, 2021.
  \url{https://github.com/TheEntityCircle/miniscience-4th-term/blob/master/2021/04_microproject/README.md}

\bibitem{gcm3drepo}
  Avasyukov A.
  \textit{gcm-3d: ani3d model.}
  GitHub repository.
  \href{https://github.com/avasyukov/gcm-3d/tree/markered-corpse/models/ani3d}{github.com/avasyukov/gcm-3d}.

\bibitem{fenicsxfusrepo}
  Adeebkor.
  \textit{fenicsx-fus.}
  GitHub repository.
  \href{https://github.com/adeebkor/fenicsx-fus}{github.com/adeebkor/fenicsx-fus}.

\bibitem{yandexdiskresults}
  \textit{Результаты моделирования в видеоформате.}
  Яндекс Диск.
  \href{https://disk.360.yandex.ru/d/l9_8UlurSN1kMA}{disk.360.yandex.ru/d/l9\_8UlurSN1kMA}.

\bibitem{matpracrepo}
  Grishin I., Votyakov A.
  \textit{matprac: материалы и код проекта.}
  GitHub repository, 2026.
  \href{https://github.com/iuriigrishin/matprac}{github.com/iuriigrishin/matprac}.

\bibitem{votyakovrepo}
  Votyakov A.
  \textit{MathPrack-S26S: материалы и код проекта.}
  GitHub repository, 2026.
  \href{https://github.com/MrVotyakov/MathPrack-S26S/}{github.com/MrVotyakov/MathPrack-S26S}.

\end{thebibliography}
